Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-15 WSSSPE3/report/wg_appendix_eng_design.tex
Update wg_appendix_eng_design.tex
Minor update

\subsection{Description of Opportunity, Challenges, and Obstacles}
The opportunity was identified to distill existing software engineering and sustainability design knowledge into ``bite sized'' chunks for the Computational Science and Engineering Community. In addition, two primary challenges were identified: 
\begin{itemize}
\item Mapping of the principles to best practice.
\item Demonstrating the return on investment of those best practices.
\end{itemize}

>>>>

\subsection{Description of Opportunity, Challenges, and Obstacles}
The opportunity was identified to distill existing software engineering and sustainability design knowledge into ''bite sized'' chunks for the Computational Science and Engineering Community. In addition, two primary challenges were identified:
\begin{itemize}
\item Mapping of the principles to best practice.
\item Demonstrating the return on investment of those best practices.
\end{itemize}
